---
title: "Network Meta Analysis, and comparisons"
author: "Joshua Edefo"
date: "2024-10-01"
email: "edefojoshua2000@yahoo.com"
output: github_document
---

```{r a, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Libraries

```{r b}
library(netmeta)
library(usethis)

```

Data for direct comparisons
```{r c}
data <- data.frame(
  study = c("Study1", "Study2", "Study3"),
  treatment1 = c("DrugA", "DrugA", "DrugB"),
  treatment2 = c("DrugB", "DrugC", "DrugC"),
  TE = c(log(1.2), log(1.4), log(0.9)), # Log-transformed effect size (e.g., log Risk Ratio)
  seTE = c(0.1, 0.12, 0.15) # Standard error of the log effect size
)
```

Perform network meta-analysis
```{r d}
nma <- netmeta(
  TE = data$TE,      # Treatment effect (log RR)
  seTE = data$seTE,  # Standard error
  treat1 = data$treatment1,  # First treatment
  treat2 = data$treatment2,  # Second treatment
  studlab = data$study,      # Study labels
  sm = "RR"                  # Summary measure: Risk Ratio
)

# Show results
print(nma)

# Plot the network
plot(nma)

# Summary of the network meta-analysis


```
Interpretation of the Indirect Comparison
Indirect RR (Drug B vs. Drug C) ≈ 1.0193: 
This indicates that, based on the indirect comparison, Drug B is associated with a 1.93% higher risk of the outcome compared to Drug C. 
However, it is crucial to analyze the confidence interval to determine significance.

Since the confidence interval for the comparison between Drug B and Drug C includes the value of 1[0.8246; 1.2601], it indicates that there is no statistically significant difference between the two treatments. This finding should prompt you to explore clinical relevance, conduct further analyses and consider additional evidence,


session information
```{r e}
sessionInfo()
```

